---
title: "Brief Tutorial on Documentation in R"
Date: June 10, 2018
bibliography: bib.bib
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
citecolor: magenta
documentclass: article # latex
fontsize: 12pt # latex
geometry: margin=1.5in # latex
header-includes: \linespread{1.25}
link-citations: yes
linkcolor: blue
citation_package: natbib # latex
params:
  stargazer_type: latex
Author: Nikhil Vidhani
urlcolor: red
---

A # followed by text becomes your title!

# Brief tutorial on R Manrkdown

Optional YAML metadata resides between two tripple dashes: `---`

Section begins by two hashes: ##

## Section 1

This is goign to be a first document.

How do we include an R code in this doc? Well just press: Ctrl-Alt-I and a code separator (three back ticks: ```) will appear!


```{r}
require(dplyr);
ns = dplyr::nasa;
ns = as.data.frame(ns);
mean_lat = mean(ns$lat, na.rm = T);
mean_lat
```

But I dont want to see all these messages in my doc. I am going to run the above with option: `include = FALSE`

```{r include = FALSE}
ns = dplyr::nasa;
ns = as.data.frame(ns);
mean_lat = mean(ns$lat, na.rm = T);
mean_lat
```

See nothing got printed above!

But I do want to display the output but not the code! Use `echo = FALSE` instead.


```{r echo = FALSE}
ns = dplyr::nasa;
ns = as.data.frame(ns);
mean_lat = mean(ns$lat, na.rm = T);
mean_lat
```

Now only the output got printed. This is what I really wanted!

What if I wanted to dynamically use a value in my doc? Like generated from a computation? We can do that by writing within backticks with first letter being `r`. So mean latitude is `r mean_lat`. This makes it very easy to update report in future with minimal changes. Lets write counting from 1 to 10: `r 1:10`

Now, let's make a plot!

```{r echo = FALSE, warning = FALSE}
ns %>% mutate(yr = year + (month-1)/12) %>% group_by(yr) %>% summarise(avg_temp = mean(surftemp), avg_pres = mean(pressure)) %>% select(avg_temp, avg_pres) %>% as.data.frame %>% plot(col = "blue", lwd = 2);
```


The plot here is a bit too big. I would like a smaller one for my doc:


```{r echo = FALSE, warning = FALSE, fig.width=5, fig.height=4, fig.cap = "avg pressure vs avg temp"}
ns %>% mutate(yr = year + (month-1)/12) %>% group_by(yr) %>% summarise(avg_temp = mean(surftemp), avg_pres = mean(pressure)) %>% select(avg_temp, avg_pres) %>% as.data.frame %>% plot(col = "blue", lwd = 2);
```


See the above fits much better!

## Section 2

To get code within the doc (in teletype constant width fonts), use single backtics: `code`, Package `dplyr`

Block quote begins with `>` sign:

> This is a block quote!

Any text within a pair of `*` is `*italicized*`: *italicized* and within `**` is `**bolded**`: **bolded**

Single star followed by a space: `* ` produces bullet points! 4 blank spaces, a star and then a space: `|    * |` produces sub-itmes! It can be further generalized!

* 1
* 2
    * 2.1
    * 2.2
        * 2.2.1


## Section 3

Math mode can be entered by writing everything within pair of dollar signs: `$`.

$F = m \cdot a$, $\lambda^2 \gamma$, $\infty$, and so on!

Write a block of equations using two dollar signs instead of one: `$$`. $$\int e^x dx = e^x + C$$.

Use underscore `_` for subscripts and exponent `^` for superscript. `H_0` is $H_0$ and `H^0` is $H^0$. Use curly brackets to combine parts of an equation, i.e. to write `lambda^(a+b)` as `\lambda^{a+b}`: $\lambda^{a+b}$


## Section 4

Use extra hash `#` for sub-sectioning.

### Sub-section 4.1
### Sub-sub-section 4.1.1
### Sub-sub-sub-section 4.1.1.1
### Sub-sub-sub-sub-section 4.1.1.1.1

## Section 5

To create a document, a process called knitting, you can simply click to knit on Rmarkdown interface. Or, you can incoke the command line: `rmarkdown::render("first_doc.Rmd")`

## Section 6

Hyperlink can be added by writing text within braces `[]` followed by the weblink written within parantheses `()`. Thus you write like: `[Google](https://www.google.com/)` to get [Google](https://www.google.com/).

Footnote can be added by `[^1]`. Here is one [^1].

[^1]: That's my foot note!

You can also add a reference using `[@bib_ref]`. For instance I'll make a reference here: [@baumer2014r]. Also don't forget to add a section on References and mention the `.bib` file in YAML metadata.

## Section 7

Let's make a table. Use the `result = "asis"` option to make sure that the table output is processed as is and not further processed!

```{r echo = FALSE, warning = F, message = F, results = "asis"}
library(stargazer);
x = rnorm(1000, 0, 1);
u = rnorm(1000, 0, 0.5);
y = u + x;
fit = lm(y ~ x);
stargazer(fit, type = params$stargazer_type, title = "Table with Stargazer in Rmarkdown")
```

## Section 8
Let's make table:

| First Header  | Second Header | Third Header         |
| :------------ | :-----------: | -------------------: |
| First row     | Data          | Very long data entry |
| Second row    | **Cell**      | *Cell*               |
| Third row     | Cell that spans across two columns  ||

Table: Your Caption

## Section 9

\begin{equation}
a=b^2
\end{equation}


# References




